%Explain the performance of the selected model on the test data, plus extra analysis if applicable. Discuss whether performace was sufficient for task.
\subsection{Caps per hour}
The selected linear model can roughly be described using:
\begin{equation}
C=65+12L-0.45\ell
\end{equation}
where $C$ is the number of caps per hour, $L$ is the dweller's Luck and $\ell$ is the starting level.\\

Mean squared error for the selected model on test data was 4.592009. Since $1\leq L\leq 10$ and $1\leq\ell\leq50$ we deduce $54.5\leq C\leq 150.5$ which means that the error is well within our demands.\\

It is a strange mechanic giving a penalty on the number of caps for high-leveled characters. We believe that the following reasons for the negative level implication are plausible:
\begin{itemize}
\item There could be some kind of extra share-out for a dweller that has just leveled up. Higher level dwellers are less likely to level up, due to the fact that the experience needed for each consecutive level increases.
\item There could be a very high chance for a share-out in the beginning of the exploration. Sincer high-level dwellers will in general survive longer, the average caps finding rate will descend as the time increases. 
\end{itemize}

\subsection{Survival time}
Estimated MSLE for the selected model on test data is 0.03785731. This corresponds to an error of around 1:10h in the average case, which is reasonable since the average survival time in the test data is 6h. In order to get a higher precision, we probably need more data.